
---
title: "Push-to-web recruitment </br> of a probability-based online panel: </br> Experimental evidence"
author: "Ulrich Krieger, Annelies Blom, Carina Cornesse, </br> Barbara Felderer, Marina Fikel </br> SFB 884 University of Mannheim"

date: "7.3.2019"
output: 
  slidy_presentation:
    font_adjustment: +2
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
```
## Outline
- Background
- Experimental Setup
- Data 
- Results
     - Recruitment interview response rate
     - Recruitment interview sample accuracy
     - Panel registration rates
     - Panel registration sample accuracy
- Summary
- Outlook

## Background
- The German Internet Panel study is a large-scale, nationwide, probability based online panel
- recruitment usinf **face-to-face** interviews in 2012, refreshment sample in 2014
- **face-to-face** 
    - helped draw a probability based sample
    - are expensive, come with interviewer effects, combined response rates relative low
- Exploring different options for 2018 refreshment sample:
- **push-to-web:** "... using mail contact to request responses over the internet while withholding alternative answering modes until later in the implementation process." (Dillman 2017)

## Push-to-web
- Implemented in large cale survey programms: 
    - European Value Survey (EVS; Roberts, Joye and Staehli 2016?)
    - American Community Survey (ACS) 
    - UK Community Life Survey (United Kingdom Cabinet Office 2016)
    - Official Censuses 
        - Japan (Statistics Japan 2015), 
        - Canada (Statistics Canada 2016)
        - Australia (Australian Bureau of Statistics 2016)
        
## ![](https://brand.wsu.edu/wp-content/themes/brand/images/pages/logos/wsu-shield-mark.svg) push-to-web study sequences  
- (eg. Dillman, Smyth, Christian 2014)
- Mail contacts inviting sample members to participate online
- later mailings included paper questionnaires.
- Findings: 
    - Overall response rate:  concurrent > mail > p2w
    - p2w leads to highest online participation rates

## push-to-web in a recruitment survey
- Adress based sample of 12,000 individuals
- all contacted by mail 
- randomly assigned to one of the groups
    - online only
    - online first
    - offline first
    - concurrent first


## Test

```{r}
knitr::include_graphics("response_rates_online1_both_phases.pdf")
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```
##test

## Slide with Plot

```{r pressure}
plot(pressure)
```

